---
title: "hw-01"
author: "Your Name (S2206199)"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}    
knitr::opts_chunk$set(out.width = "100%")
```


------------------------------------------------------------------------------

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse)
library(lubridate)

edibnb <- read_csv("data/edibnb.csv")
council <- read_csv("data/council_assessments.csv")
```

------------------------------------------------------------------------------


## EXERCISE 1

```{r hw1-ex1}
# 
missing_values <- colSums(is.na(edibnb))
print(names(missing_values[missing_values > 0]))

perfect_reviews <- edibnb[edibnb$review_scores_rating == 100, ]
  listing_with_highest_perfect_reviews <- perfect_reviews$id[which.max(table(perfect_reviews$id))]
  print(listing_with_highest_perfect_reviews)


```

The variables which have the missing observations, i.e. NAs as an entry are: 
[1] "price"               
[2] "neighbourhood"       
[3] "bathrooms"           
[4] "bedrooms"            
[5] "beds"                
[6] "review_scores_rating"

ID of the listing that has the highest number of reviews with a perfect review score of 100% is: 51505


------------------------------------------------------------------------------

## EXERCISE 2

```{r hw1-ex2}
# 
old_town_properties <- filter(edibnb, neighbourhood == "Old Town")
  expensive_properties <-   filter(old_town_properties, price > 100)
  num_properties <- nrow(expensive_properties)
  cat("Number of Airbnb properties in Old Town with one-night price > 100 GBP:", num_properties)

southside_properties <- subset(edibnb, neighbourhood == "Southside" & accommodates >= 4)
  valid_price_properties <- southside_properties[!is.na(southside_properties$price), ]
  min_price <- min(valid_price_properties$price)
  max_price <- max(valid_price_properties$price)
  avg_price <- mean(valid_price_properties$price)
  cat("Minimum price for a single night stay for four or more people in Southside:", min_price, "GBP\n")
  cat("Maximum price for a single night stay for four or more people in Southside:", max_price, "GBP\n")
  cat("Average price for a single night stay for four or more people in Southside:", avg_price, "GBP\n")

```


Number of Airbnb properties in Old Town with one-night price > 100 GBP: 494

Minimum price for a single night stay for four or more people in Southside: 10 GBP

Maximum price for a single night stay for four or more people in Southside: 800 GBP

Average price for a single night stay for four or more people in Southside: 153.1368 GBP

------------------------------------------------------------------------------

## EXERCISE 3

```{r hw1-ex3}
# 
newington_properties <- subset(edibnb, neighbourhood == "Newington")
  bathroom_freq_table <- table(newington_properties$bathrooms)
  print(bathroom_freq_table)

```


Bathroom frequency table for properties in Newington: 
0 0.5   1 1.5   2   3 3.5 
1   3 348  48  34   3   1 

This is the code I entered for part 2 of this: 
edibnb <- edibnb %>%
+     mutate(bathrooms_rounded = ceiling(bathrooms))
listings_with_more_bathrooms <- edibnb %>%
+     filter(bathrooms_rounded > bedrooms)
count_listings_with_more_bathrooms <- nrow(listings_with_more_bathrooms)
cat("Number of listings with more bathrooms than bedrooms:", count_listings_with_more_bathrooms, "\n")

However it was refusing to knit, possibly an issue with my R studios.

------------------------------------------------------------------------------

## EXERCISE 4

```{r hw1-ex4}
# 
council$assessment_date <- as.Date(council$assessment_date, format = "%Y-%m-%d")
  properties_in_may <- sum(month(council$assessment_date) == 5)
  cat("Number of properties assessed in the month of May:", properties_in_may, "\n")
  problematic_rows <- which(is.na(as.Date(council$assessment_date, format = "%Y-%m-%d")))
  council <- council[!is.na(council$assessment_date), ]
  properties_in_may <-   sum(month(council$assessment_date) == 5)
  cat("Number of properties assessed in the month of May:", properties_in_may, "\n")


```


At first I got "NA" as my answer so I removed any rows with missing or invalid date values and tried again. The number of properties assessed in the month of may: 0

The bar chart I produced seems to be blank... I think since I also got 2 for may I've screwed something up somewhere, I'm not sure what why or how though and its 14:30!

This is the code I generated the bar chart with:
library(dplyr)
library(ggplot2)
assessed_properties <- merged_data %>%
+     filter(!is.na(assessment_date))
neighbourhood_counts <- assessed_properties %>%
+     group_by(neighbourhood) %>%
+     summarise(property_count = n())
ggplot(neighbourhood_counts, aes(x = neighbourhood, y = property_count)) +
+     geom_bar(stat = "identity", fill = "blue") +
+     xlab("Neighbourhood") +
+     ylab("Number of Assessed Properties") +
+     ggtitle("Assessed Properties by Neighbourhood") +
+     theme(axis.text.x = element_text(angle = 45, hjust = 1))

However it was refusing to knit, again.
Sorry.

------------------------------------------------------------------------------
